\chapter{Conclusions}
\label{ch:conclusion}

This thesis presented a search for heavy resonances with masses between 1 \TeV and 4 \TeV, decaying into a pair of vector bosons, predicted by beyond standard model theories. The data produced by LHC proton-proton collisions, at a center-of-mass energy $\sqrt{s}=13$ \TeV during the 2016 operations, and collected by the CMS experiment, corresponding to an integrated luminosity of 35.9 \fbinv, are analyzed. The probed final state includes the invisible decay modes of one $Z$ boson, reconstructed as a large amount of missing transverse momentum, and the hadronic decay of the other vector boson (\Z, \W), reconstructed as a large-cone jet. The collected events are divided into two purity categories, based on the substructure of the hadronically decaying \V boson. No significant excesses over the expected background are observed in the entire mass range probed by the analysis.

\noindent Depending on the resonance mass, 95\% C.L. upper limits on the cross-section of heavy spin-1 and spin-2 narrow resonances, multiplied by the branching fraction of the resonance decaying into \Z and a \W boson for a spin-1 signal, and into a pair of \Z bosons for spin-2, are set in the range $0.9$ -- $63$ \fb and in the range $0.5$ -- $40$ \fb respectively. A \Wp hypothesis is excluded up to 3.11 \TeV, in the context of the Heavy Vector Triplet model A scenario, and up to 3.41 \TeV, considering the model B scenario. A bulk graviton hypothesis, given the curvature parameter $\tilde{k}=1.0$, is excluded up to 1.14 \TeV.

\vspace*{1\baselineskip}

\noindent This is the first search for $\VZ \rightarrow q \bar{q} \nu \bar{\nu}$ performed by the CMS Collaboration at $\sqrt{s} = $ 13 \TeV. This analysis is part of a set of searches for heavy resonances decaying into dibosons. The future perspectives of the analysis consist both in the combination of this final state with other diboson searches sharing the same treatment of one boson hadronic decay (namely, the same definition of the sidebands and signal regions), and in the combination of the 2016 data with the newly collected 2017 data. The luminosity already delivered by the LHC collider in 2017 is comparable to what was collected in 2016 ($\sim 40$ \fbinv). By doubling the statistics, marginal improvements are foreseen; hence, a larger enhancement can be achieved by decreasing the impacts of the systematic uncertainties. This goal can be achieved through an interplay of novel techniques.

\noindent New ideas are currently being tested, in order to improve the jet mass resolution (recursive soft drop), suppress the pile-up contribution (PUPPI associated to SoftKiller algorithm~\cite{Cacciari:2014gra}), exploit the jet substructure and tag the nature of a large-cone jet (originating from \W, \Z, Higgs boson or top quark) with machine learning techniques. %;

\noindent Another fundamental aspect that is being discussed regards the background estimation method itself. A new approach has been adopted in the search for heavy resonances in the $VW \rightarrow q \bar{q} \ell \nu$ final state~\cite{CMS-PAS-B2G-16-029}. The signal and background distributions are extracted with a two-dimensional maximum likelihood fit to data, performed on a two-dimensional plane, whose axes are represented by the groomed large-cone jet mass (reconstructing the $V \rightarrow q \bar{q}$ decay) and the invariant mass of the resonance candidate. Signal and background pre-fit distributions are modelled as 2D templates, populated starting from simulations: each generated event is represented as a gaussian kernel, as a function of the generated \pt of the large-cone jet, properly weighted by taking into account the relative cross-section of the processes considered. Even though the \emph{$\alpha$ method} has been a baseline since Run 1 era, this new 2D fit method shows some advantages: it allows a better modelling of the correlations between the jet mass and the mass of the heavy resonance, and it does not require anymore the categorization in sidebands and signal regions ($W$, $Z$ and Higgs). The latter aspect, in particular, results into having more statistics available than splitting the dataset in sidebands, and therefore smaller statistics uncertainties; furthermore, all possible diboson signals, \textit{i.e.} $VH$ and $VV$ resonances, can be simultaneously extracted in one joint analysis. One additional advantage is that the 2D fit method can be extended into a 3D fit approach for the $VV$ and $VH$ all hadronic searches, where the probed final state consists into two large-cone jets, or for searches looking for more exotic tri-bosonic decays. Preliminary results on 3D fit methods are currently being performed and seem to be promising in terms of expected sensitivity; the next aim is testing what is the gain while performing the 2D fit in the $q \bar{q} \nu \bar{\nu}$ final state as well, since (as it can be seen from fig.~\ref{fig:theory_CMS_Diboson_Summary_HVT}) its contribution to an eventual combination is still the most sensitive in the 1 \TeV -- 3 \TeV mass range.

\clearpage

